---
title: "Extract PET Study Data"
output: html_document
---

#Load packages
```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(dplyr)
library(janitor)
library(lubridate)
library(readr)
library(tools)
library(stringr)
library(fs)
library(glue)
library(purrr)
library(jsonlite)
library(kinfitr)
library(bloodstream)
```

#Structure
##Load given data (datasets)
```{r}
data_folders <- list.dirs(
  path = "/home/jan-erik/Repositories/BIDS_Sourcedata/KIH11004", 
  recursive = FALSE,
  full.names = TRUE
)

real_subjects <- keep(data_folders, ~ file.exists(file.path(.x, "studyDB.mat")))

extract_info <- function(folder) {
  file_path <- file.path(folder, "study_variables.txt")
  
  if (!file.exists(file_path)) {
    return(tibble(
      acronym = basename(folder),
      dp1 = NA,
      dp2 = NA,
      mr = NA,
    ))
  }
  
lines <- readLines(file_path)
  
    subject_line <- str_subset(lines, "^SubjectName\\s+")
    acronym <- if (length(subject_line) > 0) {
    str_split(subject_line, "\\s+", simplify = TRUE)[1, 2]
  } else {
    basename(folder)
  }
  
  dp1 <- str_extract(str_subset(lines, "dynpet1"), "\\S+\\.v$")
  dp2 <- str_extract(str_subset(lines, "dynpet2"), "\\S+\\.v$")
  mr_date <- str_extract(str_subset(lines, "mr_date"), "\\d{8}")  
  
  tibble(
    acronym = acronym,
    dp1 = ifelse(length(dp1) > 0, dp1, NA),
    dp2 = ifelse(length(dp2) > 0, dp2, NA),
    mr = ifelse(length(mr_date) > 0, mr_date, NA),
  )
}

subject_data <- map_dfr(real_subjects, extract_info)

sub_mapping <- subject_data %>%
  distinct(acronym) %>%
  arrange(acronym) %>%
  mutate(sub = sprintf("sub-%02d", row_number()))


write_csv(sub_mapping, "../DerivedData/sub_mapping_KIH11004.csv")


subject_data <- left_join(subject_data, sub_mapping, by = "acronym")

print(subject_data)
```

###Demographic File from All_PBR28.xlsx + genotyhpesKIH11004.xlsx
```{r create big demog}
all_raw_main <- read_excel("/home/jan-erik/Repositories/PBR282BIDS/RawData/All_PBR28.xlsx") %>%
  clean_names()

sub_mapping <- sub_mapping %>%
  rename(acronym = acronym) %>%
  mutate(acronym = tolower(acronym))

sub_demog_main <- all_raw_main %>%
  mutate(acronym = tolower(acronym)) %>%
  filter(!is.na(acronym), !is.na(study), study == "KIH11004") %>%
  left_join(sub_mapping) %>%
  transmute(
    sub,
    acronym,
    study,
    patient_description = cfs_allergi_ra_pope,
    hc_pat = hc_pat,
    pet_date = pet_date,
    weight = weight_kg,
    MBq = m_bq,
    comments = comments,
  )

genotype_raw <- read_excel("/home/jan-erik/Repositories/PBR282BIDS/RawData/genotypesKIH11004.xlsx") %>%
  clean_names()

sub_demog_genotype <- genotype_raw %>%
  filter(!is.na(acronym)) %>%
  mutate(acronym = tolower(acronym)) %>%
  left_join(sub_mapping) %>%
  transmute(
    sub,
    acronym,
    study = "KIH11004",
    patient_description = ctr_pat,
    hc_pat = if_else(ctr_pat == "ctr", "HC", "Pat"),
    pet_date = pet_date,
    genotype = genotype,
    weight = NA,
    MBq = NA,
    comments = NA
  )

sub_demog <- full_join(sub_demog_main, sub_demog_genotype, by = c("acronym", "sub")) %>%
  transmute(
    sub,
    acronym,
    study = coalesce(study.x, study.y),
    patient_description = coalesce(patient_description.x, patient_description.y),
    hc_pat = coalesce(hc_pat.x, hc_pat.y),
    pet_date = coalesce(pet_date.x, pet_date.y),
    weight = coalesce(weight.x, weight.y),
    MBq = coalesce(MBq.x, MBq.y),
    genotype = genotype,
    comments = coalesce(comments.x, comments.y)
  )

write_csv(sub_demog, "../DerivedData/sub_demog_KIH11004.csv")
```

####PET Specific Demog
```{r create PET demog}
sub_demog_pet <- subject_data %>%
  mutate(acronym = tolower(acronym)) %>%  
  pivot_longer(cols = c(dp1, dp2), names_to = "ses", values_to = "v_file") %>%
  mutate(
    ses = str_remove(ses, "dp"),
    ses = as.integer(ses)
  ) %>%
  filter(!is.na(v_file)) %>%
  left_join(sub_mapping) %>%
  left_join(sub_demog) %>%
  select(sub, acronym, ses, v_file, pet_date, weight, MBq, comments, hc_pat, patient_description)

write_csv(sub_demog_pet, "../DerivedData/sub_demog_pet_KIH11004.csv")
```

####MR Specific Demog
```{r create MR demog}
sub_demog_mr <- subject_data %>%
  mutate(acronym = tolower(acronym)) %>% 
  left_join(sub_mapping) %>%
  left_join(sub_demog) %>% 
  select(sub, acronym, mr, study)

write_csv(sub_demog_mr, "../DerivedData/sub_demog_mr_KIH11004.csv")
```

####Create Sub-XX-folder structure (including anat and pet folders inside each sub-XX-folder) 
```{r, eval=FALSE}
bids_base <- "../../BIDS/KIH11004/"
sub_mapping %>%
  pull(sub) %>%
  walk(function(subfolder) {
    dir_create(file.path(bids_base, subfolder, "anat"), recurse = TRUE)
    dir_create(file.path(bids_base, subfolder, "pet"), recurse = TRUE)
  })
```


##Adding .dcm to files without it
```{r add-dcm-extension-generalised, message=TRUE}
base_path <- "/home/jan-erik/Repositories/BIDS_Sourcedata"
study_path <- file.path(base_path, "KIH11004")


actual_dirs <- list.dirs(study_path, recursive = FALSE, full.names = FALSE)

acronym_lookup <- tibble(
  acronym = tolower(actual_dirs),
  folder_name = actual_dirs
)


dicom_roots <- sub_demog_mr %>%
  filter(study == "KIH11004") %>%
  mutate(acronym = tolower(acronym)) %>%
  left_join(acronym_lookup) %>%  
  mutate(
    dicom_root = file.path(base_path, study, folder_name, "raw", "mr_dicom")
  ) %>%
  pull(dicom_root)


add_dcm_extension_recursive <- function(path) {
  if (!dir_exists(path)) {
    message(glue("Skipped: map doesn't exist: {path}"))
    return()
  }

  files <- fs::dir_ls(path, recurse = TRUE, type = "file")
  files_no_ext <- files[!str_detect(path_ext(files), "\\w+")]

  if (length(files_no_ext) > 0) {
    message(glue("{length(files_no_ext)} files without extension in: {path}"))

    walk(files_no_ext, function(f) {
      new_name <- paste0(f, ".dcm")
      file_move(f, new_name)
    })

    message("added .dcm")
  } else {
    message(glue("no files without .dcm in {path}"))
  }
}


walk(dicom_roots[file.exists(dicom_roots)], add_dcm_extension_recursive)
```

#File conversion
##Dicom to Nifty
###dcm2niix
```{r, message=TRUE, eval = FALSE}

checkLines <- TRUE

mr_paths <- sub_demog_mr %>%
  filter(study == "KIH11004") %>%
  left_join(sub_mapping) %>%      
  left_join(subject_data %>%
  select(acronym, mr))

get_dcm_folder <- function(path) {
  if (!dir_exists(path)) {
    message("Path does not exist: ", path)
    return(NA_character_)
  }

  direct_dcms <- dir_ls(path, recurse = FALSE, type = "file")
  if (any(str_detect(direct_dcms, "(?i)\\.dcm$"))) {
    return(path)
  }

  t1_dirs <- dir_ls(path, recurse = TRUE, type = "directory") %>%
    keep(~ str_detect(.x, "(?i)t1"))

  if (length(t1_dirs) == 0) return(NA_character_)

  latest_t1 <- t1_dirs[which.max(fs::file_info(t1_dirs)$modification_time)]
  return(latest_t1)
}

mr_paths %>%
  mutate(
    dicom_root = file.path(base_path, study, toupper(acronym), "raw", "mr_dicom", mr),
    t1_folder = map_chr(dicom_root, get_dcm_folder),
    output_dir = file.path("/home/jan-erik/Repositories/BIDS", study, sub, "anat"),
    out_name = paste0(sub, "_T1w")
  ) %>%
  filter(!is.na(t1_folder)) %>%
  pwalk(function(t1_folder, output_dir, out_name, sub, ...) {
    dir_create(output_dir)

    command <- paste0("dcm2niix ",
                      "-z y ",     # gzip
                      "-b y ",     # BIDS sidecar
                      "-ba n ",    # no anonymisation
                      "-o ", output_dir, " ",
                      "-f ", out_name, " ",
                      t1_folder)

    if (checkLines) {
      message(glue::glue("Would run: {command}"))
    } else {
      system(command)
      message(glue::glue("Done: {sub} -> {out_name}.nii.gz"))
    }
  })
```

###ecatpet2bids
```{r, message=TRUE, eval = FALSE}
sub_demog_pet <- read_csv("../DerivedData/sub_demog_pet_KIH11004.csv") %>%
  filter(sub == "sub-25", ses == 1) %>%
  mutate(
    study = "KIH11004",
    input_path = file.path("/home/jan-erik/Repositories/BIDS_Sourcedata", study, toupper(acronym), "raw", "pet_ecat7", v_file),
    input_path_docker = file.path("/mnt/Repositories/BIDS_Sourcedata", study, toupper(acronym), "raw", "pet_ecat7", v_file),
    output_dir = file.path("/home/jan-erik/Repositories/BIDS", study, sub, "pet", paste0("ses-", ses)),
    output_dir_docker = file.path("/mnt/Repositories/BIDS", study, sub, "pet", paste0("ses-", ses)),
    out_name = paste0(sub, "_ses-", ses, "_pet.nii.gz")
  )

script_file <- "ecatpet2bids_script.sh"
writeLines("#!/bin/bash", script_file)

checkLines <- F # F = exekvera

sub_demog_pet %>%
  pwalk(function(input_path_docker, output_dir_docker, out_name, output_dir, ...) {
    
    cmd <- glue('docker run --rm -v /home/jan-erik/Repositories:/mnt/Repositories pet2bids_container /bin/bash -c \"\n
    source /opt/conda/etc/profile.d/conda.sh && \\\\\n
    conda activate PETBIDS && \\\\\n
    ecatpet2bids {input_path_docker} --convert -n {file.path(output_dir_docker, out_name)}
\"')

    if (checkLines) {
      cmd <- paste("echo", cmd)
    }

    if (file.exists(file.path(output_dir, out_name))) {
      print(cmd)
      print("Not executing: file already exists")
    } else {
      print(cmd)
      system(cmd)
    }
  })
```


The subjects that we really want the qdaconverted data for:
 sub_demog_genotype %>% filter(hc_pat=="HC") %>% filter(genotype != "not done") %>% arrange(acronym) %>% pull(acronym)
```{r}
sub_demog_HC <- sub_demog_genotype %>% 
  filter(hc_pat=="HC") %>% 
  filter(genotype != "not done") %>% 
  arrange(acronym)

write_csv(sub_demog_HC, "../DerivedData/sub_demog_HC_KIH11004.csv")

```

###Blood
#### .QDA/.qda-converter (blood data)
# Bloodfiles HC + Parentfraction HC
```{r}
qdafiles_HC %>%
  mutate(
    ses = "1",
    ses_id = glue("ses-{ses}"),
    fullfilename = file.path("/home/jan-erik/Repositories/BIDS_Sourcedata/KIH11004/blood", glue("{acronym}_blood_qdaconverted.csv")),
    out_dir = file.path("/home/jan-erik/Repositories/BIDS/KIH11004", sub, ses_id, "pet"),
    auto_file = file.path(out_dir, glue("{sub}_{ses_id}_recording-autosampler_blood.tsv")),
    manual_file = file.path(out_dir, glue("{sub}_{ses_id}_recording-manual_blood.tsv")),
    pf_fullfilename = file.path(
      "/home/jan-erik/Repositories/BIDS_Sourcedata/KIH11004", 
      glue("{toupper(acronym)}/modelling/data/Blood_analysis_anton/{acronym}_parent_fraction.txt")
    )
  )

View(qdafiles_HC)
```

####AUTO + MANUAL + PF
```{r}
checkLines <- F

#AUTO
extract_auto_data <- function(fullfilename) {
  read_csv(fullfilename, show_col_types = FALSE) %>%
    select(`ABSS sec`, `ABSS count`, `Cbl (uncorr)`) %>%
    filter(!is.na(`ABSS count`)) %>% 
    transmute(
      time = `ABSS sec`,
      whole_blood_radioactivity = `Cbl (uncorr)` 
    )
}

#MANUAL
extract_manual_data <- function(fullfilename) {
  read_csv(fullfilename, show_col_types = FALSE) %>% 
  select(`HK_sa_min`, `HK_sa_sec`, `HK_Cbl`, `HK_Cpl`) %>% 
  filter(!is.na(`HK_Cpl`)) %>% 
    transmute( 
      time = `HK_sa_min`*60 + `HK_sa_sec`,
      whole_blood_radioactivity = `HK_Cbl`,
      plasma_radioactivity = `HK_Cpl`
    )
}

#PF
extract_pf_data <- function(pf_filename) {
  read_delim(pf_filename, delim = "\t", show_col_types = FALSE) %>% 
    rename(time = 'Time[sec]', metabolite_parent_fraction = 'Parent_fraction[1/1]') 
}  
    
  
#Merge extract_manual_data + extract_pf_data with left_join as it should match with time 
extract_combined_manual <- function(fullfilename, pf_filename) {
  manual <- extract_manual_data(fullfilename)
  pf <- extract_pf_data(pf_filename)
  left_join(manual, pf, by = "time")
}

pmap(
  list(
    fullfilename = qdafiles_HC$fullfilename,
    pf_fullfilename = qdafiles_HC$pf_fullfilename,
    auto_file = qdafiles_HC$auto_file,
    manual_file = qdafiles_HC$manual_file,
    out_dir = qdafiles_HC$out_dir
  ),

  function(fullfilename, pf_fullfilename, auto_file, manual_file, out_dir) {
    
  if (checkLines) {
      message(glue::glue("  [AUTO]   {auto_file}"))
      message(glue::glue("  [MANUAL] {manual_file}"))
    } else {
      
      fs::dir_create(out_dir)
      auto_df <- extract_auto_data(fullfilename)
      readr::write_tsv(auto_df, auto_file)
      
      manual_df <- extract_combined_manual(fullfilename, pf_fullfilename)
      readr::write_tsv(manual_df, manual_file)
    }
  }
)
```

#####.Json sidecar (Auto)
```{r}
pwalk(
  list(
    autosampler_file = qdafiles_HC$auto_file,
    sub = qdafiles_HC$sub,
    ses_id = qdafiles_HC$ses_id,
    out_dir = qdafiles_HC$out_dir
  ),
  function(autosampler_file, sub, ses_id, out_dir) {
    
    blood_df <- read_tsv(autosampler_file, show_col_types = FALSE)
 
    blood_df$whole_blood_radioactivity <- unit_convert(
      values = blood_df$whole_blood_radioactivity,
      from_units = "nCi",
      to_units = "Bq"
    )
    
    json_filename <- glue("sub-{sub}_{ses_id}_recording-autosampler_blood.json")
    json_path <- file.path(out_dir, json_filename)
    
    auto_sidecar <- list(
      PlasmaAvail = FALSE,
      MetaboliteAvail = FALSE,
      WholeBloodAvail = TRUE,
      DispersionCorrected = FALSE,
      DispersionConstant = 2.5991,
      time = list(
        Description = "Time in relation to time zero defined by the _pet.json",
        Units = "s"
      ),
      whole_blood_radioactivity = list(
        Description = "Radioactivity in whole blood samples. Measured using Allogg autosampler.",
        Units = "Bq/mL"
      )
    )
    write_json(auto_sidecar, path = json_path, pretty = TRUE, auto_unbox = TRUE)
  }
)

```

#####.Json sidecar (Manual)
```{r}
pwalk(
  list(
    manual_file = qdafiles_HC$manual_file,
    sub = qdafiles_HC$sub,
    ses_id = qdafiles_HC$ses_id,
    out_dir = qdafiles_HC$out_dir
  ),
  function(manual_file, sub, ses_id, out_dir) {
    blood_df <- read_tsv(manual_file, show_col_types = FALSE)

    blood_df$whole_blood_radioactivity <- unit_convert(
      blood_df$whole_blood_radioactivity,
      from_units = "nCi",
      to_units = "Bq"
    )

    blood_df$plasma_radioactivity <- unit_convert(
      blood_df$plasma_radioactivity,
      from_units = "nCi",
      to_units = "Bq"
    )

    json_filename <- glue("sub-{sub}_{ses_id}_recording-manual_blood.json")
    json_path <- file.path(out_dir, json_filename)

    manual_sidecar <- list(
      PlasmaAvail = TRUE,
      WholeBloodAvail = TRUE,
      MetaboliteAvail = TRUE,
      MetaboliteMethod = "HPLC",
      MetaboliteRecoveryCorrectionApplied = FALSE,
      DispersionCorrected = FALSE,
      time = list(
        Description = "Time in relation to time zero defined in _pet.json",
        Units = "s"
      ),
      plasma_radioactivity = list(
        Description = "Radioactivity in plasma samples.",
        Units = "Bq/mL"
      ),
      metabolite_parent_fraction = list(
        Description = "Parent fraction of Radio tracer",
        Units = "arbitrary"
      ),
      whole_blood_radioactivity = list(
        Description = "Radioactivity in whole blood samples. Measured using Allogg autosampler.",
        Units = "Bq/mL"
      )
    )

    write_json(manual_sidecar, path = json_path, pretty = TRUE, auto_unbox = TRUE)
  }
)
```

## Blood unit fixing

**Note:** We find that the blood units seem to be out. It may be that the TACs are actually in the wrong units, but for now we have corrected the blood data. We have done so by multiplying by 37.


NOTE: NEVER RUN THIS AGAIN!!!

[x] Done

```{r, eval=FALSE}
autoblood <- list.files("../../BIDS/KIH11004/", recursive=T, pattern="autosampler_blood.tsv", full.names = T)
manblood <- list.files("../../BIDS/KIH11004/", recursive=T, pattern="manual_blood.tsv", full.names = T)

fixmanblood <- function(filename) {
  dat <- read_tsv(filename)
  dat$whole_blood_radioactivity <- dat$whole_blood_radioactivity*37
  dat$plasma_radioactivity <- dat$plasma_radioactivity*37
  write_tsv(dat, filename)
}

for(i in 1:length(manblood)) {
  print(i)
  fixmanblood(manblood[i])
}


fixautoblood <- function(filename) {
  
  dat <- read_tsv(filename)
  dat$whole_blood_radioactivity <- dat$whole_blood_radioactivity*37
  # dat$plasma_radioactivity <- dat$plasma_radioactivity*37
  
  write_tsv(dat, filename)
}

for(i in 1:length(autoblood)) {
  print(i)
  fixautoblood(autoblood[i])
}
```

#BIDS APPS FOR PET - Processing
##MR Processing
###sMRIPrep
Ran this in Terminal (enter correct environment first: conda activate PETBIDS)
```{bash, eval=FALSE}
smriprep-docker \
  --fs-license-file /home/jan-erik/Documents/FreeSurfer/license.txt \
  /home/jan-erik/Repositories/BIDS/KIH11004 \
  /home/jan-erik/Repositories/BIDS/KIH11004/derivatives \
  participant \
  --nprocs 32 \
  --omp-nthreads 16 \
  --mem-gb 90 \
  --output-spaces MNI152NLin2009cAsym:res-1 anat
```

###petprep_hmc
```{r}
system("rm --r ../../BIDS/KIH11004/sub-25/ses-1/")
```

####Fixing Folder tree stucture for the PET-files in order to use petprep_hmc
```{r}

base_dir <- "/home/jan-erik/Repositories/BIDS/KIH11004"

subject_dirs <- list.dirs(base_dir, recursive = FALSE, full.names = TRUE)
subject_dirs <- subject_dirs[grepl("^sub-\\d+", basename(subject_dirs))]

for (subj in subject_dirs) {
  pet_dir <- file.path(subj, "pet")
  if (!dir_exists(pet_dir)) next
  
  session_dirs <- list.dirs(pet_dir, recurse = FALSE, full.names = TRUE)
  
  for (ses_path in session_dirs) {
    ses_name <- basename(ses_path)  # t.ex. "ses-1"
    
    new_pet_dir <- file.path(subj, ses_name, "pet")
    dir_create(new_pet_dir, recursive = TRUE)
    
    files_to_move <- dir_ls(ses_path, type = "file", recurse = FALSE)
    file_move(files_to_move, file.path(new_pet_dir, basename(files_to_move)))
    
    if (length(dir_ls(ses_path)) == 0) {
      dir_delete(ses_path)
    }
  }
  
  if (length(dir_ls(pet_dir)) == 0) {
    dir_delete(pet_dir)
    message(glue::glue("Removed empty folder: {pet_dir}"))
  }
}

```

#####run petprep_hmc
```{bash}
docker run --rm \
-v /home/jan-erik/Repositories/BIDS/KIH11004:/data/input \
-v /home/jan-erik/Repositories/BIDS/KIH11004/derivatives/petprep_hmc:/data/output \
-v /home/jan-erik/Documents/FreeSurfer/license.txt:/opt/freesurfer/license.txt \
martinnoergaard/petprep_hmc:latest \
/data/input /data/output participant --participant_label sub-25 
```



###petprep_extract_tacs (using petprep_hmc files)
```{bash}
docker run -a stderr -a stdout --rm \
-v /home/jan-erik/Repositories/BIDS/KIH11004:/bids_dir \
-v /home/jan-erik/Repositories/BIDS/KIH11004/derivatives/petprep_extract_tacs:/output_dir \
-v $PWD:/workdir -v /home/jan-erik/Repositories/petprep_extract_tacs:/petprep_extract_tacs \
-v /home/jan-erik/Documents/FreeSurfer/license.txt:/opt/freesurfer/license.txt \
--platform linux/amd64 \
petprep_extract_tacs \
/bids_dir /output_dir participant --participant_label sub-25 --n_procs 10 --gtm  --petprep_hmc 
```

#Blood processing
## See "Modelling.Rmd"


```{r}
extra_info <- read_excel("/home/jan-erik/Repositories/PBR282BIDS/RawData/Subjects_PET_MR_info.xlsx") %>%
  rename(
    acronym = Acronym,
    Age = Age,
    MBq = `PBR28, Inj. Activity (MBq)`
  ) %>%
  mutate(acronym = tolower(acronym)) %>%
  filter(acronym %in% tolower(qdafiles_HC$acronym)) %>%  
  select(acronym, Age, MBq)


sub_demog_pet_extended <- sub_demog %>%
  filter(acronym %in% qdafiles_HC$acronym) %>%
  left_join(qdafiles_HC %>% select(acronym, ses), by = "acronym") %>%
  left_join(extra_info, by = "acronym", suffix = c("", ".new")) %>%
  mutate(
    pet_date = as.Date(pet_date),
    weight = NA,
    comments = NA,
    male1_female2 = NA,
    MBq = coalesce(MBq, MBq.new),  
    Age = round(Age)
  ) %>%
  select(
    sub,
    acronym,
    study,
    ses,
    pet_date,
    weight,
    MBq,
    comments,
    genotype,
    male1_female2,
    Age
  ) %>% 
  rename(Genotype = genotype)

write_csv(sub_demog_pet_extended, "/home/jan-erik/Repositories/PBR282BIDS/DerivedData/sub_demog_pet_extended_KIH11004.csv")
```


# Combined Demographic of data from the two studies used for modelling
```{r}
library(writexl)
demog_11004 <- read.csv("/home/jan-erik/Repositories/PBR282BIDS/DerivedData/sub_demog_pet_extended_KIH11004.csv")
demog_12001 <- read.csv("/home/jan-erik/Repositories/PBR282BIDS/DerivedData/sub_demog_pet_extended_KIH12001.csv")

PBR28_combined_demograph <- dplyr::bind_rows(demog_11004, demog_12001)

write_xlsx(PBR28_combined_demograph, "/home/jan-erik/Repositories/PBR282BIDS/RawData/PBR28_combined_demograph_KIH11004_KIH12001.xlsx")
```

















