---
title: "Extract PET Study Data"
output: html_document
---

#Load packages
```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(dplyr)
library(janitor)
library(lubridate)
library(readr)
library(stringr)
library(fs)
library(glue)
library(purrr)
library(jsonlite)
library(kinfitr)
library(bloodstream)
library(furrr)
```

#Structure
##Load given data (datasets)
```{r}
dataSet <- list.files(
  path = "/mnt/alfred/Atlas_Images/KIH12001/",
  pattern = "^[a-zA-Z]{4}$",
  full.names = TRUE
)
```

###Identify Real Subjects
```{r}
real_subjects <- vector()

for (folder in dataSet) {
  if (file.exists(file.path(folder, "studyDB.mat"))) {
    real_subjects <- c(real_subjects, folder)
  }
}

real_subjects_names <- basename(real_subjects)

sub_mapping <- tibble(
  acronym = sort(unique(tolower(real_subjects_names))),
  sub = sprintf("%02d", 1:length(acronym))
)

# Save for reference
write_csv(sub_mapping, "../DerivedData/sub_mapping_KIH12001.csv")

```

###Extract Information from Study Variables
```{r}
extract_info <- function(folder) {
file_path <- file.path(folder, "study_variables.txt")
  
  if (!file.exists(file_path)) {
    return(tibble(Subject_Folder = basename(folder), DP1 = NA, DP2 = NA, MR = NA))
  }
  
  lines <- readLines(file_path)
  
  dp1 <- str_extract(str_subset(lines, "dynpet1"), "\\S+\\.v$")
  dp2 <- str_extract(str_subset(lines, "dynpet2"), "\\S+\\.v$")
  
  mr_date <- str_extract(str_subset(lines, "mr_date"), "\\d{8}")  
  
  tibble(
    Subject_Folder = basename(folder),
    DP1 = ifelse(length(dp1) > 0, dp1, NA),
    DP2 = ifelse(length(dp2) > 0, dp2, NA),
    MR = ifelse(length(mr_date) > 0, mr_date, NA)
  )
}

subject_data <- map_dfr(real_subjects, extract_info)
print(subject_data)
```

###Demographic File from All_PBR28.xlsx
```{r create big demog}
all_raw <- read_excel("/home/jan-erik/Repositories/PBR282BIDS/RawData/All_PBR28.xlsx") %>% clean_names()

sub_demog <- all_raw %>%
  filter(!is.na(acronym), !is.na(study)) %>%
  left_join(sub_mapping) %>%
  transmute(
    sub,      
    acronym,         
    study,
    patient_description = cfs_allergi_ra_pope,
    hc_pat = hc_pat
  )

write_csv(sub_demog, "../DerivedData/sub_demog_KIH12001.csv")
```


####PET Specific Demog
```{r create PET demog}
sub_demog_pet <- all_raw %>%
  filter(!is.na(acronym), !is.na(study)) %>%
  left_join(sub_mapping) %>%
  transmute(
    sub,
    acronym,
    study,
    ses = pet1_pet2_pet3,
    pet_date = pet_date, 
    weight = weight_kg,
    MBq = m_bq,
    comments = comments
  )

write_csv(sub_demog_pet, "../DerivedData/sub_demog_pet_KIH12001.csv")
```


```{r}

extrainfo_genotype_sex <- read_excel("/home/jan-erik/Repositories/PBR282BIDS/RawData/PBR28_database_demograph_genotype.xlsx") %>%
  rename(acronym = Subjects) %>%
  distinct(acronym, Genotype, male1_female2, .keep_all = FALSE)

extra_demog2 <- read_excel("/home/jan-erik/Repositories/PBR282BIDS/RawData/PET_group_gene_EVF_170215.xlsx") %>%
  rename(acronym = Acronym) %>% 
  mutate(
    male1_female2 = case_when(
      Kön == "Man" ~ 1,
      Kön == "Kvinna" ~ 2,
      TRUE ~ NA_real_
    ),
    
    Genotype = case_when(
      Genotyp == "A/A" ~ "LAB",
      Genotyp == "A/G" ~ "MAB",
      Genotyp == "G/G" ~ "HAB",
      TRUE ~ NA_character_
    )
  ) %>% 
  select(acronym, Age = Ålder, Genotype, male1_female2, PET1, PET2)

extra_combined <- full_join(extrainfo_genotype_sex, extra_demog2, by = "acronym", suffix = c("", ".new")) %>%
  mutate(
    Genotype = coalesce(Genotype, Genotype.new),
    male1_female2 = coalesce(male1_female2, male1_female2.new),
    Age = Age,

    PET1 = suppressWarnings(case_when(
      is.na(PET1) ~ NA_Date_,
      !is.na(as.numeric(PET1)) ~ as.Date(as.numeric(PET1), origin = "1899-12-30"),
      TRUE ~ parse_date_time(PET1, orders = c("mdy", "m/d/y"))
    )),
    PET2 = suppressWarnings(case_when(
      is.na(PET2) ~ NA_Date_,
      !is.na(as.numeric(PET2)) ~ as.Date(as.numeric(PET2), origin = "1899-12-30"),
      TRUE ~ parse_date_time(PET2, orders = c("mdy", "m/d/y"))
    ))
  ) %>%
  select(acronym, Genotype, male1_female2, Age, PET1, PET2)


sub_demog_pet_extended <- sub_demog_pet %>%
  filter(study == "KIH12001") %>%
  left_join(extra_combined, by = "acronym") %>%
  mutate(
    sub = str_pad(as.character(sub), width = 2, pad = "0"),
    pet_date = as.Date(pet_date),
    pet_date = case_when(
      is.na(pet_date) & ses == 1 & !is.na(PET1) ~ as.Date(PET1),
      is.na(pet_date) & ses == 2 & !is.na(PET2) ~ as.Date(PET2),
      TRUE ~ pet_date
    )
  ) %>%
  select(sub, acronym, study, ses, pet_date, weight, MBq, comments,
         Genotype, male1_female2, Age)


write_csv(sub_demog_pet_extended,"/home/jan-erik/Repositories/PBR282BIDS/DerivedData/sub_demog_pet_extended_KIH12001.csv")
```

####MR Specific Demog
```{r create MR demog}
subject_data_clean <- subject_data %>%
  transmute(
    acronym = tolower(Subject_Folder),
    mr_date = MR
  )

full_subject_list <- all_raw %>%
  filter(!is.na(acronym), !is.na(study)) %>%
  select(acronym, study) %>%
  distinct()

sub_demog_mr <- full_subject_list %>%
  left_join(sub_mapping) %>%
  left_join(subject_data_clean) %>% 
  select(sub, acronym, study, mr_date) %>%
  arrange(sub)

write_csv(sub_demog_mr, "../DerivedData/sub_demog_mr_KIH12001.csv")
```


####Create Sub-XX-folder structure (including anat and pet folders inside each sub-XX-folder) 
```{r, eval=FALSE}
bids_base <- "../../BIDS/KIH12001/"
sub_mapping %>%
  pull(sub) %>%
  paste0("sub-", .) %>%
  walk(function(subfolder) {
    dir_create(file.path(bids_base, subfolder, "anat"), recurse = TRUE)
    dir_create(file.path(bids_base, subfolder, "pet"), recurse = TRUE)
  })
```


#MR

```{r, eval=FALSE}
mr_sequences = sub_demog_mr %>% 
  group_by(sub) %>% 
  mutate(
    dicom_dir = glue("/mnt/alfred/Atlas_Images/KIH12001/{acronym}/raw/mr_dicom/"),
    output_dir = glue("../../BIDS/{study}/{sub}/anat/")
  ) 

  saveRDS(mr_sequences, "../DerivedData/mr_sequences_KIH12001.rds")
  
```


##Filter for T1w MR subjects
```{r}
mr_sequences <- readRDS("../DerivedData/mr_sequences_KIH12001.rds") 
  
mr_sequences_t1 <- mr_sequences %>%
  mutate(
    t1w = any(str_detect(dir(dicom_dir, full.names = FALSE, recursive = TRUE), regex("t1")))
  ) %>% 
  ungroup() %>% 
  filter(t1w)
```



##Adding .dcm to files without it
```{r add-dcm-extension-generalised, message=TRUE}
base_path <- "/home/jan-erik/Repositories/BIDS_Sourcedata"

dicom_roots <- sub_demog_mr %>%
  filter(study == "KIH12001") %>%
  mutate(
    dicom_root = file.path(base_path, study, acronym, "raw", "mr_dicom")
  ) %>%
  pull(dicom_root)

add_dcm_extension_recursive <- function(path) {
  files <- fs::dir_ls(path, recurse = TRUE, type = "file")
  files_no_ext <- files[!str_detect(path_ext(files), "\\w+")]

  if (length(files_no_ext) > 0) {
    message(glue("{length(files_no_ext)} files without extension in: {path}"))

    walk(files_no_ext, function(f) {
      new_name <- paste0(f, ".dcm")
      file_move(f, new_name)
    })

    message("Added extensions.")
  } else {
    message(glue("No extensionless files in: {path}"))
  }
}

walk(dicom_roots, add_dcm_extension_recursive)
```

##Find T1 folder for every subject
```{r find-t1-folder-generalised, message=TRUE}
base_path_KIH12001 <- "/mnt/alfred/Atlas_Images" 

mr_paths <- sub_demog_mr %>%
  filter(study == "KIH12001") %>%
  mutate(
    dicom_root = file.path(base_path_KIH12001, study, acronym, "raw", "mr_dicom")
  ) %>%
  rowwise() %>%
  mutate(
    t1_folder = list(
      fs::dir_ls(dicom_root, recurse = TRUE, type = "directory") %>%
        keep(~ str_detect(.x, regex("t1|T1|DICOM", ignore_case = FALSE))) %>%
        head(1)
    ),
    t1_folder = ifelse(length(t1_folder) == 0, NA, t1_folder)
  ) %>%
  ungroup()
```

#Dicom to Nifty
##dcm2niix
```{r, message=TRUE, eval = F}
checkLines <- F

mr_paths %>%
  filter(study == "KIH12001") %>%
  filter(!is.na(t1_folder)) %>%
  mutate(
    output_dir = file.path("/home/jan-erik/Repositories/BIDS", study, paste0("sub-", sub), "anat"),
    out_name = paste0("sub-", sub, "_T1w")
  ) %>%
  pwalk(function(t1_folder, output_dir, out_name, sub, ...) {
    message(glue::glue("Converting T1 for {sub}..."))

    command <- paste0("dcm2niix ", 
      "-z ", "y ",              # gzip compression
      "-b ", "y ",              # BIDS sidecar (JSON)
      "-ba ", "n ",             # no anonymisation
      "-o ", output_dir, " ",   # output goes to pre-created anat folder
      "-f ", out_name, " ",     # correct BIDS name
      t1_folder                 # input DICOM folder
    )
    
    if(checkLines==T) { command <- paste0("echo ", command) }
    
    system(command)

    message(glue::glue("Klar: {sub} → {output_dir}/{out_name}.nii.gz + .json"))
  })
```


#Processing
##MR Processing
```{bash, eval=FALSE}
smriprep-docker --fs-license-file /home/jan-erik/Documents/FreeSurfer/license.txt /home/jan-erik/Repositories/BIDS/KIH12001 /home/jan-erik/Repositories/BIDS/KIH12001/derivatives participant
```

###ecatpet2bids
```{r, message=TRUE}
checkLines <- T

subject_data_petlong <- subject_data %>%
  pivot_longer(cols = c(DP1, DP2), names_to = "ses", values_to = "v_file") %>%
  mutate(
    ses = str_remove(ses, "DP"),
    ses = as.integer(ses)
  ) %>%
  filter(!is.na(v_file)) %>%
  rename(acronym = Subject_Folder) %>% 
  left_join(sub_mapping) %>%
  select(sub, ses, v_file) %>% 
  mutate(ses = as.character(ses))

sub_demog_pet <- sub_demog_pet %>%
  left_join(subject_data_petlong) %>%
  filter(!is.na(v_file)) 

sub_demog_pet <- sub_demog_pet %>%
  mutate(
    input_path = file.path("/home/jan-erik/Repositories/BIDS_Sourcedata", study, acronym, "raw", "pet_ecat7", v_file),
    input_path_docker = file.path("/mnt/Repositories/BIDS_Sourcedata", study, acronym, "raw", "pet_ecat7", v_file),
    output_dir = file.path("/home/jan-erik/Repositories/BIDS", study, paste0("sub-", sub), "pet", paste0("ses-", ses)),
    output_dir_docker = file.path("/mnt/Repositories/BIDS", study, paste0("sub-", sub), "pet", paste0("ses-", ses)),
    out_name = paste0("sub-", sub, "_ses-", ses, "_pet.nii.gz")
  )

script_file <- "ecatpet2bids_script.sh"
writeLines("#!/bin/bash", script_file)

sub_demog_pet %>%
  pwalk(function(input_path_docker, output_dir_docker, out_name, output_dir, ...) {
    
    cmd <- glue('docker run --rm -v /home/jan-erik/Repositories:/mnt/Repositories pet2bids_container /bin/bash -c \"\n
    source /opt/conda/etc/profile.d/conda.sh && \\\\\n
    conda activate PETBIDS && \\\\\n
    ecatpet2bids {input_path_docker} --convert -n {file.path(output_dir_docker, out_name)}
\"')

    if (checkLines) cmd <- paste("echo", cmd)
    
    if(file.exists( file.path(output_dir, out_name)) ) {
      
      print(cmd)
      print("Not executing: file already exists")
      
    } else {
      
      print(cmd)
      system(cmd)
      
    }
  })
```

## .QDA/.qda-converter (blood data)
```{r}
blood_data <- sub_demog %>% 
  group_by(sub) %>% 
  transmute(
    acronym,
    study,
    blood_dir = glue("/mnt/alfred/Atlas_Images/{study}/{acronym}/modelling/data/") 
  )

qda_roots <- blood_data %>%
  filter(study == "KIH12001") %>%
  mutate(
    qda_root = file.path(base_path_KIH12001, study, acronym, "modelling", "data")
  ) %>% 
  pull(qda_root)

#funktion för att köra alla .qda filer genom funktionen "qda_jailbreak.R"
run_qda_jailbreak_recursive <- function(path) {
  qda_files <- fs::dir_ls(path, recurse = T, type = "file")
  
  # Välj ut de filer med .qda/.QDA-ändelse
  files_with_qda_QDA <- qda_files[str_detect(path_ext(qda_files), "(?i)qda")]
  
  
    if(length(files_with_qda_QDA) > 0) {
    # Source the jailbreak function
    source("qda_jailbreak.R")
    
    # Apply the function to each QDA file
    purrr::walk(files_with_qda_QDA, ~qda_jailbreak(.x, outputdir = "../../BIDS_Sourcedata/KIH12001/blood/"))
    
      message("qda_jailbreak.R executed on all .qda/.QDA files")
  } else {
    message(glue("No .QDA/.qda files found in: {path}"))
  }
}


purrr::walk(qda_roots, run_qda_jailbreak_recursive)
```

```{r}
mr_sequences_t1 <- mr_sequences %>%
  mutate(
    t1w = any(str_detect(dir(dicom_dir, full.names = FALSE, recursive = TRUE), regex("t1")))
  ) %>% 
  ungroup() %>% 
  filter(t1w)
```

#Extracting blood data
```{r}
qdafiles <- tibble(
  fullfilename = list.files(
    path = "/home/jan-erik/Repositories/BIDS_Sourcedata/KIH12001/blood",  
    pattern = "qdaconverted.csv", 
    recursive = TRUE, full.names = TRUE)
) %>%
  mutate(
    filename = basename(fullfilename),
    filepath = dirname(fullfilename),
    acronym = str_match(filename, "([a-z]*)_\\d")[, 2],
    ses = str_match(filename, "[a-z]*_(\\d)")[, 2]
  ) %>%
  mutate(
    pf_fullfilename = map2_chr(acronym, ses, ~ {
      search_dir <- "/mnt/alfred/Atlas_Images/KIH12001"
      id <- paste0(.x, "_", .y)
      files <- list.files(
        path = search_dir,
        pattern = paste0("^", id, "_parent_fraction\\.txt$"),
        full.names = TRUE,
        recursive = TRUE,
        ignore.case = TRUE
      )
      if (length(files) == 0) NA_character_ else files[1]
    })
  ) %>%
  left_join(sub_mapping, by = "acronym") %>%
  mutate(
    ses_id = glue("ses-{ses}"),
    out_dir = file.path("/home/jan-erik/Repositories/BIDS/KIH12001",glue("sub-{sub}"), ses_id, "pet"),    
    auto_file = file.path(out_dir, glue("sub-{sub}_{ses_id}_recording-autosampler_blood.tsv")),
    manual_file = file.path(out_dir, glue("sub-{sub}_{ses_id}_recording-manual_blood.tsv"))
  )
```

##AUTO + MANUAL + PF
```{r}
checkLines <- F

#AUTO
extract_auto_data <- function(fullfilename) {
  read_csv(fullfilename, show_col_types = FALSE) %>%
    select(`ABSS sec`, `ABSS count`, `Cbl (uncorr)`) %>%
    filter(!is.na(`ABSS count`)) %>% 
    transmute(
      time = `ABSS sec`,
      whole_blood_radioactivity = `Cbl (uncorr)` 
    )
}

#MANUAL
extract_manual_data <- function(fullfilename) {
  read_csv(fullfilename, show_col_types = FALSE) %>% 
  select(`HK_sa_min`, `HK_sa_sec`, `HK_Cbl`, `HK_Cpl`) %>% 
  filter(!is.na(`HK_Cpl`)) %>% 
    transmute(
      time = `HK_sa_min`*60 + `HK_sa_sec`,
      whole_blood_radioactivity = `HK_Cbl`,
      plasma_radioactivity = `HK_Cpl`
    )
}

#PF
extract_pf_data <- function(pf_filename) {
  read_delim(pf_filename, delim = "\t", show_col_types = FALSE) %>% 
    rename(time = 'Time[sec]', metabolite_parent_fraction = 'Parent_fraction[1/1]') 
}  
    
  
#Merge extract_manual_data + extract_pf_data with left_join as it should match with time 
extract_combined_manual <- function(fullfilename, pf_filename) {
  manual <- extract_manual_data(fullfilename)
  pf <- extract_pf_data(pf_filename)
  left_join(manual, pf, by = "time")
}

pmap(
  list(
    fullfilename = qdafiles$fullfilename,
    pf_fullfilename = qdafiles$pf_fullfilename,
    auto_file = qdafiles$auto_file,
    manual_file = qdafiles$manual_file,
    out_dir = qdafiles$out_dir
  ),

  function(fullfilename, pf_fullfilename, auto_file, manual_file, out_dir) {
    
  if (checkLines) {
      message(glue::glue("  [AUTO]   {auto_file}"))
      message(glue::glue("  [MANUAL] {manual_file}"))
    } else {
      
      fs::dir_create(out_dir)
      auto_df <- extract_auto_data(fullfilename)
      readr::write_tsv(auto_df, auto_file)
      
      manual_df <- extract_combined_manual(fullfilename, pf_fullfilename)
      readr::write_tsv(manual_df, manual_file)
    }
  }
)
```


###.Json sidecar (Auto)
```{r}
pwalk(
  list(
    autosampler_file = qdafiles$auto_file,
    sub = qdafiles$sub,
    ses_id = qdafiles$ses_id,
    out_dir = qdafiles$out_dir
  ),
  function(autosampler_file, sub, ses_id, out_dir) {
    
    blood_df <- read_tsv(autosampler_file, show_col_types = FALSE)
 
    blood_df$whole_blood_radioactivity <- unit_convert(
      values = blood_df$whole_blood_radioactivity,
      from_units = "nCi",
      to_units = "Bq"
    )
    
    json_filename <- glue("sub-{sub}_{ses_id}_recording-autosampler_blood.json")
    json_path <- file.path(out_dir, json_filename)
    
    auto_sidecar <- list(
      PlasmaAvail = FALSE,
      MetaboliteAvail = FALSE,
      WholeBloodAvail = TRUE,
      DispersionCorrected = FALSE,
      DispersionConstant = 2.5991,
      time = list(
        Description = "Time in relation to time zero defined by the _pet.json",
        Units = "s"
      ),
      whole_blood_radioactivity = list(
        Description = "Radioactivity in whole blood samples. Measured using Allogg autosampler.",
        Units = "Bq/mL"
      )
    )
    write_json(auto_sidecar, path = json_path, pretty = TRUE, auto_unbox = TRUE)
  }
)

```

###.Json sidecar (Manual)
```{r}
pwalk(
  list(
    manual_file = qdafiles$manual_file,
    sub = qdafiles$sub,
    ses_id = qdafiles$ses_id,
    out_dir = qdafiles$out_dir
  ),
  function(manual_file, sub, ses_id, out_dir) {
    blood_df <- read_tsv(manual_file, show_col_types = FALSE)

    blood_df$whole_blood_radioactivity <- unit_convert(
      blood_df$whole_blood_radioactivity,
      from_units = "nCi",
      to_units = "Bq"
    )

    blood_df$plasma_radioactivity <- unit_convert(
      blood_df$plasma_radioactivity,
      from_units = "nCi",
      to_units = "Bq"
    )

    json_filename <- glue("sub-{sub}_{ses_id}_recording-manual_blood.json")
    json_path <- file.path(out_dir, json_filename)

    manual_sidecar <- list(
      PlasmaAvail = TRUE,
      WholeBloodAvail = TRUE,
      MetaboliteAvail = TRUE,
      MetaboliteMethod = "HPLC",
      MetaboliteRecoveryCorrectionApplied = FALSE,
      DispersionCorrected = FALSE,
      time = list(
        Description = "Time in relation to time zero defined in _pet.json",
        Units = "s"
      ),
      plasma_radioactivity = list(
        Description = "Radioactivity in plasma samples.",
        Units = "Bq/mL"
      ),
      metabolite_parent_fraction = list(
        Description = "Parent fraction of Radio tracer",
        Units = "arbitrary"
      ),
      whole_blood_radioactivity = list(
        Description = "Radioactivity in whole blood samples. Measured using Allogg autosampler.",
        Units = "Bq/mL"
      )
    )

    write_json(manual_sidecar, path = json_path, pretty = TRUE, auto_unbox = TRUE)
  }
)
```

## Blood unit fixing

**Note:** We find that the blood units seem to be out. It may be that the TACs are actually in the wrong units, but for now we have corrected the blood data. We have done so by multiplying by 37.


NOTE: NEVER RUN THIS AGAIN!!!

[x] Done

```{r, eval=FALSE}
autoblood <- list.files("../../BIDS/KIH12001/", recursive=T, pattern="autosampler_blood.tsv", full.names = T)
manblood <- list.files("../../BIDS/KIH12001/", recursive=T, pattern="manual_blood.tsv", full.names = T)

fixmanblood <- function(filename) {
  
  dat <- read_tsv(filename)
  dat$whole_blood_radioactivity <- dat$whole_blood_radioactivity*37
  dat$plasma_radioactivity <- dat$plasma_radioactivity*37
  
  write_tsv(dat, filename)
}

for(i in 1:length(manblood)) {
  print(i)
  fixmanblood(manblood[i])
}


fixautoblood <- function(filename) {
  
  dat <- read_tsv(filename)
  dat$whole_blood_radioactivity <- dat$whole_blood_radioactivity*37
  # dat$plasma_radioactivity <- dat$plasma_radioactivity*37
  
  write_tsv(dat, filename)
}

for(i in 1:length(autoblood)) {
  print(i)
  fixautoblood(autoblood[i])
}
```


#HMC
##Fixing Folder tree stucture for the PET-files in order to use petprep_hmc
```{r}
base_dir <- "/home/jan-erik/Repositories/BIDS/KIH12001" 

subject_dirs <- list.dirs(base_dir, recursive = FALSE, full.names = TRUE)
subject_dirs <- subject_dirs[grepl("sub-\\d+", basename(subject_dirs))]

for (subj in subject_dirs) {
  pet_path <- file.path(subj, "pet")
  
  if (!dir.exists(pet_path)) next
  
  session_dirs <- list.dirs(pet_path, recursive = FALSE, full.names = TRUE)
  
  for (ses_path in session_dirs) {
    ses_name <- basename(ses_path)
    files <- list.files(ses_path, full.names = TRUE)
    
    new_dir <- file.path(subj, ses_name, "pet")
    dir.create(new_dir, recursive = TRUE, showWarnings = FALSE)
    
    for (file in files) {
      new_file <- file.path(new_dir, basename(file))
      file.rename(file, new_file)
    }
    
    if (length(list.files(ses_path)) == 0) {
      dir_delete(ses_path, recursive = TRUE)
    }
  }
}

subject_dirs <- list.dirs(base_dir, recursive = FALSE, full.names = TRUE)
subject_dirs <- subject_dirs[grepl("sub-\\d+", basename(subject_dirs))]

for (subj in subject_dirs) {
  pet_path <- file.path(subj, "pet")
  
  if (dir.exists(pet_path)) {
    if (length(list.files(pet_path, recursive = TRUE)) == 0) {
      unlink(pet_path, recursive = TRUE)
      message(sprintf("Removed empty folder: %s", pet_path))
    }
  }
}
```

###petprep_hmc
```{bash}
rm -rf /home/jan-erik/Repositories/BIDS/KIH12001/sub-03/ses-2 

docker run -it --rm \
-v /home/jan-erik/Repositories/BIDS/KIH12001:/data/input \
-v /home/jan-erik/Repositories/BIDS/KIH12001/derivatives/petprep_hmc:/data/output \
-v /home/jan-erik/Documents/FreeSurfer/license.txt:/opt/freesurfer/license.txt \
martinnoergaard/petprep_hmc:latest \
/data/input /data/output group --n_procs 10
```

#TAC (using petprep_hmc files)
```{bash}
docker run -a stderr -a stdout --rm \
-v /home/jan-erik/Repositories/BIDS/KIH12001:/bids_dir \
-v /home/jan-erik/Repositories/BIDS/KIH12001/derivatives/petprep_extract_tacs:/output_dir \
-v $PWD:/workdir -v /home/jan-erik/Repositories/petprep_extract_tacs:/petprep_extract_tacs \
-v /home/jan-erik/Documents/FreeSurfer/license.txt:/opt/freesurfer/license.txt \
--platform linux/amd64 \
petprep_extract_tacs \
/bids_dir /output_dir participant --participant_label sub-03 --n_procs 10 --gtm  --petprep_hmc
```






























